The mass distribution of companions to low-mass white dwarfs

### 2014-10-23 documents/letter/ms.tex
Updated .tex

\bibitem[{{Benvenuto} \& {De Vito}(2005)}]{benvenuto05}
{Benvenuto}, O.~G., \& {De Vito}, M.~A. 2005, \mnras, 362, 891

@@

@@

\bibitem[{{Jia} \& {Li}(2014)}]{jia14}
{Jia}, K., \& {Li}, X.-D. 2014, \apj, 791, 127

@@

\bibitem[{{Liebert} {et~al.}(2005){Liebert}, {Bergeron}, \&
  {Holberg}}]{liebert05}
{Liebert}, J., {Bergeron}, P., \& {Holberg}, J.~B. 2005, \apjs, 156, 47

>>>>

\bibitem[{{Brown} {et~al.}(2006){Brown}, {Geller}, {Kenyon}, \&
  {Kurtz}}]{brown06}
{Brown}, W.~R., {Geller}, M.~J., {Kenyon}, S.~J., \& {Kurtz}, M.~J. 2006, \apj,
  647, 303

@@

\bibitem[{{Eisenstein} {et~al.}(2006){Eisenstein}, {Liebert}, {Harris},
  {Kleinman}, {Nitta}, {Silvestri}, {Anderson}, {Barentine}, {Brewington},
  {Brinkmann}, {Harvanek}, {Krzesi{\'n}ski}, {Neilsen}, {Long}, {Schneider}, \&
  {Snedden}}]{eisenstein06}
{Eisenstein}, D.~J. {et~al.} 2006, \apjs, 167, 40

@@

@@

\bibitem[{{Liebert} {et~al.}(2004){Liebert}, {Bergeron}, {Eisenstein},
  {Harris}, {Kleinman}, {Nitta}, \& {Krzesinski}}]{liebert04}
{Liebert}, J., {Bergeron}, P., {Eisenstein}, D., {Harris}, H.~C., {Kleinman},
  S.~J., {Nitta}, A., \& {Krzesinski}, J. 2004, \apjl, 606, L147
